Title

### 2013-03-22 inc/hardware/deflector/deflector.tex
added some content, but also restructured some of the folders related to hardware
minor tweaks to deflector section

In order to redirect the beam down the column, in conjunction with the accelerator alignment mechanisms, custom large area deflector plates were employed.
Four plates are arranged on a hollow tube with a square profile, one on each side.
One of each pair is held at ground while the other has a variable potential.
By varying each potential the beam may be turned in flight.

@@

A schematic description of such a system is shown in \ref{fig:deflector_schematic}.
To estimate the required voltage on the plates $V$, consider the applied impulse provided to the beam by the plate's electric field
\begin{gather}
  F \Delta t = m \Delta v \\
  \frac{ e V }{ d } \frac{ L }{ v_z } = m_e \Delta v_x
\end{gather}
where (as seen in the figure) $L$ is the length of the plate (in the direction of travel $\hat{z}$) and $d$ is the separation of the plates.
Then in the small angle approximation, the angle that the plate may correct for is approximately
\begin{equation}
  \theta = \frac{ \Delta v_x }{ v_z } = \frac{ e }{ m_e } \frac{ L }{ d } \frac{ V }{ v_z^2 }
\end{equation}
Using this result, when $L \sim d$ and $v_z = c/3$ a voltage of 1kV will deflect the beam approximately one degree.
These plates therefore are used as a fine adjustment, as opposed to the coarse adjustment provided by aligning the acceleration gap.

\begin{figure}
  \centering
  \includegraphics{deflector_plates.jpg}
  \caption[Picture of custom deflector plates]{
    Picture of the custom built deflector plates for use in the UEM at UIC.
    A pair of vertical and horizontal plates are mounted in a non-conductive housing.
    Each plate has a pin for connecting to voltage or ground.
    Clearance drilled holes allow mounting onto the ``eV parts'' cage inside the chamber.
  }
  \label{fig:deflector-plates-pic}
\end{figure}

>>>>

In order to redirect the beam down the column, custom large area deflector plates were employed in conjunction with the gross accelerator alignment mechanism described earlier.
Four plates are arranged on a hollow tube with a square profile, one on each side.
One of each pair is held at ground while the other has a variable potential.
By varying each potential the beam may be turned in flight.

@@

A schematic description of such a system is shown in \ref{fig:deflector_schematic}.
To estimate the required voltage on the plates $V$, consider the applied impulse provided to the beam by the plate's electric field
\begin{gather}
  F \Delta t = m \Delta v \\
  \frac{ e V }{ d } \frac{ L }{ v_z } = m_e \Delta v_x
\end{gather}
where (as seen in the figure) $L$ is the length of the plate (in the direction of travel $\hat{z}$) and $d$ is the separation of the plates.
Then in the small angle approximation, the angle that the plate may correct for is approximately
\begin{equation}
  \theta = \frac{ \Delta v_x }{ v_z } = \frac{ e }{ m_e } \frac{ L }{ d } \frac{ V }{ v_z^2 }
\end{equation}
Using this result, when $L \sim d$ and $v_z = c/3$ a voltage of 1kV will deflect the beam approximately one degree.
These plates are, therefore, useful as a fine beam adjustment, as contrast to the coarse adjustment provided by manually aligning the acceleration gap.

\begin{figure}
  \centering
  \includegraphics{deflector_plates.jpg}
  \caption[Picture of custom deflector plates]{
    Picture of the custom built deflector plates for use in the UEM at UIC.
    A pair of vertical and horizontal plates are mounted in a non-conductive housing.
    Each plate has a pin for connecting to voltage or ground.
    Clearance drilled holes allow mounting onto the ``eV Parts'' cage inside the chamber.
  }
  \label{fig:deflector-plates-pic}
\end{figure}
